### 2016-12-20 R/ITHIM.Rmd
Version 0.2 has almost made it through ITHIM.Rmd and ITHIM2.Rmd error-free

  ITHIM.national <- update(ITHIM.national, "muNonTravel", muNonTravel)

@@

@@

ITHIMListScenario <- lapply(ITHIMList, function(ithim) update(ithim, parName = "muwt", parValue = ithim@parameters@muwt + 10*7))

@@

```{r California, eval = TRUE, dev=c('pdf', 'png'), fig.width = fig.width, fig.asp = phi, warning = FALSE, message = FALSE, echo = FALSE}
ITHIM.national <- update(ITHIM.national, parName = "muNonTravel", 10)

@@

ITHIM.CA <- ITHIMList[["CA"]]
ITHIM.CA <- update(ITHIM.CA, parName = "muNonTravel", 10)
foo1 <- compareModels(ITHIM.national,ITHIM.CA)
foobar1 <- data.frame(cbind(melt(foo1$daly.delta),paste0("ageClass",1:8)),State = "CA")

@@

ITHIM.NY <- ITHIMList[["NY"]]
ITHIM.NY <- update(ITHIM.NY, parName = "muNonTravel", 10)
foo2 <- compareModels(ITHIM.national,ITHIM.NY)
foobar2 <- data.frame(cbind(melt(foo2$daly.delta),paste0("ageClass",1:8)),State = "NY")
foobar <- rbind(foobar1,foobar2)
names(foobar) <- c("delta.DALY","Sex","Disease","ageClass","State")

@@

```{r methodsPaper, eval = TRUE, dev=c('pdf', 'png'), fig.width = fig.width, fig.asp = 1/phi, warning = FALSE, message = FALSE, echo = FALSE}
ITHIM.default <- update(ITHIM.default, "quantiles", (1:99)/100)

ITHIM.national <- ITHIM.default
ITHIM.national <- update(ITHIM.national, "muwt", muwtNational)
ITHIM.national <- update(ITHIM.national, "muct", muctNational)
ITHIM.national <- update(ITHIM.national, "Rwt", RwtNational)
ITHIM.national <- update(ITHIM.national, "Rct", RctNational)

ITHIM.scenario <- ITHIM.national
ITHIM.national.quints <- update(ITHIM.national, "quantiles", seq(1,9,by=1)/10)
ITHIM.scenario.quints <- update(ITHIM.scenario, "quantiles", seq(1,9,by=1)/10)

@@

    ITHIM.scenario <- update(ITHIM.scenario, "muwt", at*pWalk)
    ITHIM.scenario <- update(ITHIM.scenario, "muct", at*(1-pWalk))
    ITHIM.scenario <- update(ITHIM.scenario, "muNonTravel", muNonTravel)

    ITHIM.scenario.quints <- update(ITHIM.scenario.quints, "muwt", at*pWalk)
    ITHIM.scenario.quints <- update(ITHIM.scenario.quints, "muct", at*(1-pWalk))
    ITHIM.scenario.quints <- update(ITHIM.scenario.quints, "muNonTravel", muNonTravel)

    ITHIM.national <- update(ITHIM.national, "muNonTravel", muNonTravel)

@@

ITHIM.national <- update(ITHIM.national, "muNonTravel", 10)

>>>>

  ITHIM.national <- update(ITHIM.national, list(muNonTravel = muNonTravel))

@@

saveRDS(ITHIMList, file = "./data/ITHIMList.by.state.rds")

@@

ITHIMListScenario <- lapply(ITHIMList, function(ithim) update(ithim, list(muwt = ithim@parameters@muwt + 10*7)))

@@

```{r California, eval = TRUE, dev=c('pdf', 'png'), fig.width = fig.width, fig.asp = phi, warning = FALSE, message = FALSE, echo = FALSE}
ITHIM.national <- update(ITHIM.national, list(muNonTravel = 10))

@@

ITHIM.CA <- ITHIMList[["CA"]]
ITHIM.CA <- update(ITHIM.CA, list(muNonTravel = 10))
foo1 <- compareModels(ITHIM.national,ITHIM.CA)
foobar1 <- data.frame(cbind(melt(foo1$daly.delta),paste0("ageClass",1:8)),State = "CA")

@@

ITHIM.NY <- ITHIMList[["NY"]]
ITHIM.NY <- update(ITHIM.NY, list(muNonTravel = 10))
foo2 <- compareModels(ITHIM.national,ITHIM.NY)
foobar2 <- data.frame(cbind(melt(foo2$daly.delta),paste0("ageClass",1:8)),State = "NY")
foobar <- rbind(foobar1,foobar2)
names(foobar) <- c("delta.DALY","Sex","Disease","ageClass","State")

@@

```{r methodsPaper, eval = TRUE, dev=c('pdf', 'png'), fig.width = fig.width, fig.asp = 1/phi, warning = FALSE, message = FALSE, echo = FALSE}
ITHIM.default <- update(ITHIM.default, list(quantiles = (1:99)/100))

ITHIM.national <- ITHIM.default
ITHIM.national <- update(ITHIM.national, list(muwt = muwtNational, muct = muctNational,Rwt = RwtNational,Rct = RctNational))

ITHIM.scenario <- ITHIM.national
ITHIM.national.quints <- update(ITHIM.national, list(quantiles = seq(1,9,by=2)/10))
ITHIM.scenario.quints <- update(ITHIM.scenario, list(quantiles = seq(1,9,by=2)/10))

@@

    ITHIM.scenario <- update(ITHIM.scenario, list(muwt = at*pWalk, muct = at*(1-pWalk), muNonTravel = muNonTravel))

    ITHIM.scenario.quints <- update(ITHIM.scenario.quints, list(muwt = at*pWalk, muct = at*(1-pWalk), muNonTravel = muNonTravel))

    ITHIM.national <- update(ITHIM.national, list(muNonTravel = muNonTravel))

@@

ITHIM.national <- update(ITHIM.national, list(muNonTravel = 10))
